---
title: "Class 1 - Multisensory integration instructions"
author: "Sigrid Agersnap Bom Nielsen"
date: "15/9/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE) 
```

```{r}
pacman::p_load(tidyverse, readbulk, patchwork, lmerTest)
```

Here, we'll try to replicate some cross modal effects.

First of all, you need to download the data from the google drive folder: https://drive.google.com/drive/folders/1JCYyynaXQ4TUxXk0UJhBf7BN_q3sSPWJ 

Hint: you can use read_bulk() from the readbulk package to load the different csv files into one dataframe (one df for vision, one for audition). 

If you're up for a challenge you can also write code which loads all the data into one dataframe (there is a column called 'version', which helps to tell the data set apart).

```{r}
#loading data
df_vis <- read_bulk('/Users/magnus.k.sigaard/Google Drev/CogSci/3. semester/Perception and Action/Class/Class_tutorials/2021_09_17_C1/Vision')
df_aud <- read_bulk('/Users/magnus.k.sigaard/Google Drev/CogSci/3. semester/Perception and Action/Class/Class_tutorials/2021_09_17_C1/Audition') 
```

Before you start looking at the data, discuss what predictions you have and why. 

# Investigate the data
Each row is one trial. RT is measured in milliseconds.

What variables do we have? Which ones are we interested in? Do we need to change the format of some of them?

```{r}
# get a glimpse of the data
glimpse(df_aud)
glimpse(df_vis)


```

Try to make a plot of the mean reaction times per congruency. You might want to remove incorrect trials.

Interpret the findings. Do they match your predictions? Why? Why not? 

```{r}
# Removing incorrect trials
df_vis <- df_vis %>% filter(accuracy != "false")

# Cleaning
df_vis <- df_vis %>% 
  mutate(
    accuracy = as.factor(accuracy),
    congruency = as.factor(congruency),
    subject = as.factor(subject))

########################## PLOTTING TIME ##################################

df_vis %>%
  ggplot(aes(congruency, rt))+
  geom_boxplot()

df_vis %>%
  ggplot(aes(congruency, rt))+
  stat_summary(fun = "mean", geom = "point")+
  stat_summary(fun = "sd", geom = "line")


## ########################### Sigrids solution

# AUDITION
data_audition %>% 
  filter(accuracy == 'TRUE') %>% 
  ggplot() +
  aes(x = congruency, y = rt, fill = congruency) + 
  geom_boxplot() +
  theme(legend.position = 'None') +
  labs(title = 'Audition RT')

# VISION
data_vision %>% 
  filter(accuracy == 'TRUE') %>% 
  ggplot() + 
  aes(x = congruency, y = rt, fill = congruency) + 
  geom_boxplot() +
  theme(legend.position = 'None') +
  labs(title = 'Vision RT')


################# Mean reaction times with error bars

# Audition
data_audition %>% 
  filter(accuracy == 'TRUE') %>% 
  ggplot() +
  aes(x = congruency, y = rt, color = congruency) +
  stat_summary(fun = "mean", geom = "point", size = 3) +
  stat_summary(fun = 'mean', geom = 'line', color = 'gray55', aes(group = 1)) +
  stat_summary(fun.data = "mean_se", geom = "errorbar", width = .1) +
  theme(legend.position = 'None') +
  labs(title = 'Mean RT of audition with SE errorbars')

# Vision
data_vision %>% 
  filter(accuracy == 'TRUE') %>% 
  ggplot() +
  aes(x = congruency, y = rt, color = congruency) +
  stat_summary(fun = "mean", geom = "point", size = 3) +
  stat_summary(fun = 'mean', geom = 'line', color = 'gray55', aes(group = 1)) +
  stat_summary(fun.data = "mean_se", geom = "errorbar", width = .1) +
  theme(legend.position = 'None') +
  labs(title = 'Mean RT of vision with SE errorbars')


################### Mean RT per subject
### RT per subject - vision
plot_rt_vis <- data_vision %>% 
   group_by(subject, congruency) %>% 
   filter(accuracy == 'TRUE') %>%
   summarize(mean_rt = mean(rt)) %>%
  ggplot() + 
  aes(x=congruency, y=mean_rt, color=subject) + 
  geom_point() + 
  geom_line(aes(group=subject))

### RT per subject - audition
plot_rt_aud <- data_audition %>% 
   group_by(subject, congruency) %>% 
   filter(accuracy == 'TRUE') %>%
   summarize(mean_rt = mean(rt)) %>%
  ggplot() + 
  aes(x=congruency, y=mean_rt, color=subject) + 
  geom_point() + 
  geom_line(aes(group=subject))

plot_rt_vis + plot_rt_aud
```

# CHALLENGE LEVEL 1 - Modelling time
Does congruency predict the reaction time?

Try making a simple linear model. Here, you should consider removing the incorrect trials.

```{r}

```

# CHALLENGE LEVEL 2 - Accuracy rate
Make a graph of accuracy rate. Can you visualize the relationship between congruency and the percentage of incorrectly answered trials per subject?

Discuss the resulting plots. 

```{r}

```


