---
title: "W4_mouse tracking data"
author: "Magnus K. Sigaard"
date: "10/15/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Packages

```{r}
pacman::p_load(mousetrap, dplyr)
```

# Data

```{r}
df <- read.csv("subject-3.csv")
glimpse(df)
```

## Turning data into mousetrap object
```{r}
?mt_import_mousetrap
mtd <- mt_import_mousetrap(df)
```

# Plots
## 2. Basic plot
```{r}
mt_plot(mtd)
```
This plot shows the mouse path of participants.
Here, the mouse movements are inverted. 

## Aggregated trajectory plot
```{r}
mt_plot_aggregate(mtd)
```
**Im not sure how this is to be interpreted**

## Adding rectangles to trajectory plot
```{r}
#mt_plot_add_rect(mtd)
```
Does not work .. dont know why.



## Plotting per trajectory
```{r}
#mt_plot_per_trajectory(data = mtd)
```



## 3. Plotting by trial type
```{r}
plot_bytrial <- mt_plot(mtd, color = "trial_type")
plot_bytrial
```

## 4. Symmetric plotting
```{r}
# Pushing all data to one side
mtd <- mt_remap_symmetric(mtd,
                   use = "trajectories",
                   remap_xpos = "left")

# Plotting it
mt_plot(mtd, color = "trial_type")
```

## 5. Timestamp plot
```{r}
mt_plot(mtd,
        x = "timestamps",
        y = "xpos",
        use = "trajectories",
        color = "trial_type")
```
The line in the beginning must be the time spent on not moving the mouse? Holding the mouse still.
After some time, participants start moving their mouses to either the left-hand or right-hand side.

## 6. Removing the initial line
```{r}
# Excluding initiations
mtd <- mt_exclude_initiation(mtd)
?mt_exclude_initiation

# Plotting
mt_plot(mtd,
        x = "timestamps",
        y = "xpos",
        use = "trajectories",
        color = "trial_type")
```

# 7. Normalizing time data
```{r}
mtd_norm <- mt_time_normalize(mtd)
mtd_norm1 <- mt_time_normalize(mtd, nsteps = 10)
```

## 8. Plotting normalized data
```{r}
mt_plot(mtd_norm1,
        x = "timestamps",
        y = "xpos",
        use = "trajectories",
        color = "trial_type")
```

## 9. Changing number of steps
```{r}
mtd_norm2 <- mt_time_normalize(mtd, nsteps = 10)
mt_plot(mtd_norm2,
        x = "timestamps",
        y = "xpos",
        use = "tn_trajectories",
        color = "trial_type")
mtd_norm3 <- mt_time_normalize(mtd, nsteps = 100)
mt_plot(mtd_norm3,
        x = "timestamps",
        y = "xpos",
        use = "tn_trajectories",
        color = "trial_type")
```
We see a more straight curve for the small number of nsteps.


