---
title: "Simon Task"
author: "Sigrid Agersnap Bom Nielsen"
date: "8/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# load packages
pacman::p_load(tidyverse, wesanderson, lmerTest, readbulk)
```

Data can be found here: <https://drive.google.com/drive/folders/18hTvraUiPwxfzCzXl0QNP0Nh5LQK2Oql?usp=sharing>

```{r}
# load data
d <- read_bulk(
  directory = 'data/',
  fun = read_csv
  )
```

# Getting to know the data
First, take a look at the data. Which columns do we have? Which ones do we need to examine if there is in fact a Simon Task effect? 

```{r}
glimpse(d)
```

# Creating a congruency column 
In order to examine the data, we need to create a congruency column, which indicates whether the trial in question is congruent, incongruent or neutral. 

Hint: you can do this by making a ifelse statement using the existing columns 'color' and 'position'. 

```{r}
d <- d %>% 
  mutate(
    congruency = ifelse(
      color == 'green' & position == 'left' | color == 'red' & position == 'right', 'congruent', 'incongruent'),
    congruency = ifelse(position == 'middle', 'neutral', congruency),
    congruency = as.factor(congruency),
    accuracy = as.factor(accuracy)
  )
```

# Removing 'training' trials

```{r}
# we only want the test trials 
d <- d %>% 
  filter(
    part == 'test'
    )
```

# Plotting time! 
- Visualize the mean RT of each congruency category with SE error bars (you might want to remove incorrect trials for this one).

```{r}
# getting a nice Wes Anderson color palette

# I like this one
wes_palette('Darjeeling1')

# save it in a variable to be used when plotting
pal <- wes_palettes$Darjeeling1
```

```{r}
################ plotting mean RT with SE errorbars
d %>% 
  filter(
    accuracy == 'TRUE'
    ) %>% 
ggplot() + 
  aes(x = congruency, y = rt, color = congruency) +
  # creating the geom points of the mean rt of  each congruency
  stat_summary(fun = "mean", geom = "point", size = 3, color = pal[1:3]) +
  # adding the error bars
  stat_summary(fun.data = "mean_se", geom = "errorbar", width = .1, color = pal[1:3]) +
  # adding the connecting line between the points 
  stat_summary(fun = 'mean', geom = 'line', color = pal[5], aes(group = 1)) +
  theme(legend.position = 'None') +
  labs(title = 'Mean RT of the Simon Task with SE errorbars')

```
- Visualize the accuracy for each congruency

```{r}
############### Plotting accuracy and congruency
d %>% 
  ggplot() +
  aes(accuracy, fill = congruency) + 
  geom_bar() + 
  facet_grid(~ congruency) +
  scale_fill_manual(values = pal) +
  labs(title = 'Accuracy for each congruency') + 
  theme(legend.position = 'NULL')
```

# Challenge level 1: Modelling time

 - Does congruency predict the reaction time? 
 
```{r}
# as you guys are very smart and know about the possible pitfalls of using p-values, we'll make a simple model using the much discussed p-values
m1 <- lmerTest::lmer(rt ~ congruency + (1|subject), d)
summary(m1)
```

- Does congruency predict accuracy? 

```{r}
# this time we have a logistic regression with random effects, why the glmer() is being used
m2 <- glmer(accuracy ~ congruency + (1 | subject), data = d, family = binomial)
summary(m2)
```

# Challenge level 2: Play with palettes 
Go back to your plot and try to change the colors using a specific palette, e.g. a palette from the wesanderson package. 
Make your plots look their best ;-)
