---
title: "Simon Task"
author: "Sigrid Agersnap Bom Nielsen"
date: "8/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# load packages
pacman::p_load(...)
```

Data can be found here: <https://drive.google.com/drive/folders/18hTvraUiPwxfzCzXl0QNP0Nh5LQK2Oql?usp=sharing>

```{r}
# load data
```

# Getting to know the data
First, take a look at the data. Which columns do we have? Which ones do we need to examine if there is in fact a Simon Task effect? 

```{r}
```

# Creating a congruency column 
In order to examine the data, we need to create a congruency column, which indicates whether the trial in question is congruent, incongruent or neutral. 

Hint: you can do this by making a ifelse statement using the existing columns 'color' and 'position'. 

```{r}
```

# Removing 'training' trials

```{r}
```

# Plotting time! 
- Visualize the mean RT of each congruency category with SE error bars (you might want to remove incorrect trials for this one).

```{r}

```

- Visualize the accuracy for each congruency

```{r}

```

# Challenge level 1: Modelling time

 - Does congruency predict the reaction time? 
 
```{r}

```

- Does congruency predict accuracy? 

```{r}

```

# Challenge level 2: Play with palettes 
Go back to your plot and try to change the colors using a specific palette, e.g. a palette from the wesanderson package. 
Make your plots look their best ;-)
